\documentclass{resume}
\usepackage[utf8]{inputenc}
\usepackage[linewidth=0.65pt]{mdframed}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{fontawesome}
\usepackage{hyperref}

% Item-less subsection
\newenvironment{rEmptySubsubsection}[2]{
    {\em #1\/} \hfill {\em #2\/} % Italic job name and date on the right
    }

    \name{Jason Kölker}
    \address{\
        \faEnvelope\ \href{mailto:jason@koelker.net}{jason@koelker.net}
        \hspace{2mm}
        \faMobile\ \href{tel:+1 210 264 5113}{+1 210 264 5113}
        \hspace{2mm}
        \faGithub\ \href{https://github.com/jkoelker}{jkoelker}
    }

    \begin{document}

    \begin{rSection}{Summary}
        Skilled IT strategist and solution developer, with more than 15 years of
        cross-platform expertise and a strong background in software and networking
        development. Red Hat Certified Engineer, with fluency in multiple programming
        languages and a diverse skill set encompassing software defined networking,
        data storage and backup, and fleet automation.
    \end{rSection}

    \begin{rSection}{Technical Highlights}
        \bigskip
        \mdfdefinestyle{techskills}{innerleftmargin=0.5em,innerrightmargin=0.5em}
        \begin{mdframed}[style=techskills]
            \begin{tabular}{l l}
                {\bf Cloud:} & AWS, GCP, Azure, OpenStack \\
                {\bf Containers:} & Kubernetes, Podman, Docker \\
                {\bf Languages:} & Go, Python, C, C++, Java, C\#, bash, Erlang \\
                {\bf Networking:} & VxLAN, OpenVswitch, OpenFlow, STT, BGP, EVPN \\
                {\bf Services:} & Apache/nginx, Bind, OpenLDAP, Active Directory,
                ElasticSearch, HAProxy \\
                {\bf Systems:} & Linux, Windows, *BSD, Solaris \\
            \end{tabular}
        \end{mdframed}
    \end{rSection}

    \begin{rSection}{Experience}
        \begin{rSubsection}{Lambda}
            {2024 -- Present} % chktex 8
            {San Jose, CA -- Remote} % chktex 8
            \begin{rSubsubsection}{Staff Software Engineer} % chktex 8
                {2024 -- Present} % chktex 8
            \item Run Lambda’s Neutron/OVN‑based SDN stack for the GPU cloud,
                hardening and operating deployments across thousands of nodes
                while maintaining strict multi‑tenant isolation.
            \item Designed and implemented an API‑driven DirectConnect /
                Interconnect platform that enables self service
                ingress/egress from isolated tenant networks to external
                environments via BGP/MPLS, WireGuard, VPNs, or any
                interface presented connection, unlocking new enterprise
                connectivity options.
            \item Built CI, deployment, and versioning pipelines for the SDN
                stack, reducing manual intervention and making software
                rollouts repeatable and auditable.
            \item Introduced automatic version management with Renovate for
                networking components, enabling faster upgrades, reduced
                security exposure, and lower maintenance toil for the SDN and
                DPU software ecosystem.
            \item Serve as the subject matter expert for NVIDIA DPUs and the
                DOCA platform, owning the networking roadmap and integration
                with other teams, and routinely consulting on architecture
                and implementation patterns for high‑performance cloud
                networking.
            \end{rSubsubsection}
        \end{rSubsection}
        \begin{rSubsection}{Twilio}
            {2023 -- 2024} % chktex 8
            {San Francisco, CA -- Remote} % chktex 8
            \begin{rSubsubsection}{Principal Software Engineer} % chktex 8
                {2023 -- Present} % chktex 8
            \item Implement next generation streaming platform for Twilio
                Segment. Develop APIs and SDKs to enable developers to focus
                on business logic, instead of streaming infrastructure.
            \item Provide technical leadership and mentoring to a team of
                engineers.
            \item Build composable CDP platform allowing for activation on
                data sourced from customer warehouses.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{Impossible Cloud}
            {2023 -- 2023} % chktex 8
            {Hamburg, Germany -- Remote} % chktex 8
            \begin{rSubsubsection}{Principal Software Engineer} % chktex 8
                {2023 -- 2023} % chktex 8
            \item Implement multi-region, multi-cloud object replication system.
            \item Architect Poof of Concept S3 compatible storage platform using
                IPFS and Filecoin for persistence.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{FloatMe}
            {2021 -- 2023} % chktex 8
            {San Antonio, TX -- Remote} % chktex 8
            \begin{rSubsubsection}{Principal Software Engineer} % chktex 8
                {2022 -- Present} % chktex 8
            \item Architect streaming processing system for data ingestion
                and notification between micro-services.
            \item Implement Developer and QA driven release process simplifying
                code deployment.
            \end{rSubsubsection}
            \begin{rSubsubsection}{Staff Software Engineer} % chktex 8
                {2021 -- 2022} % chktex 8
            \item Re-Architect App from monolith code base to micro-services.
            \item Champion repo organization with a focus on CI/CD, developer
                productivity, and Infrastructure as Code.
            \item Institute ``Guild'' system for cross team collaboration and
                specialization.
            \item Redesign authentication system to proxy through CloudFlare
                workers, providing additional tools to prevent abuse.
            \item Implement mTLS between app and API with option for
                certificate rotation outside of app deployment life cycle.
            \item Co-Lead with Head of Product re-organization of product
                and development interaction with a focus on agile software
                development.
            \item Provide Technical Leadership and Mentoring growing team from
                7 Software Engineers to over 30. Define roles and levels for
                Engineering Org providing clear responsibilities and career
                progression path.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{Banadushi Enterprises LLC}
            {2008 -- Present} % chktex 8
            {Live Oak, TX -- Remote} % chktex 8
            \begin{rSubsubsection}{Software Engineering Consultant} % chktex 8
                {2008 -- Present} % chktex 8
            \item Various consulting activities related to distributed
                systems, software development, devops, and automation.
            \item Specializing in Kubernetes, ClusterAPI, and OS Image
                Generation for clients.
            \end{rSubsubsection}
        \end{rSubsection}
        \begin{rSubsection}{D2iQ / Mesosphere}
            {2018 -- 2021} % chktex 8
            {San Francisco, CA -- Remote} % chktex 8
            \begin{rSubsubsection}{Senior Software Engineer -- Mesosphere} % chktex 8
                {2020 -- 2021} % chktex 8
            \item Took over maintenance and Point of Escalation duties for the DCOS
                Network stack.
            \item Worked with customers and stakeholders to standardize Edge-LB
                ``Self-Service'' and set deprecation schedule for Marathon-LB\@.
            \item Ensured continuity of support for customers via on-call and
                escalations, troubleshooting the entirety of the DCOS stack.
            \end{rSubsubsection}
            \begin{rSubsubsection}{Senior Software Engineer -- Kubernetes} % chktex 8
                {2019 -- 2020} % chktex 8
            \item Spearheaded CI testing of charts for Pull Requests and main branch.
            \end{rSubsubsection}
            \begin{rSubsubsection}{Senior Software Engineer -- Networking} % chktex 8
                {2018 -- 2019} % chktex 8
            \item Lead development efforts of ``Self-Service'' Edge-LB\@. Defined Mesos
                task labels to drive templated Edge-LB pool configuration, allowing
                end users to expose their applications automatically.
            \item Championed maintenance of Marthon-LB\@. Reviewed and merged backlog of
                community contributions, refactoring where needed to work with current
                project codebase.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{ColorBit LLC}
            {2017 -- 2025} % chktex 8
            {Midlothian, TX -- Remote} % chktex 8
            \begin{rSubsubsection}{Co-Owner / Technical Lead}
                {2017 -- 2025} % chktex 8
            \item Developed patent pending LED light controller. Leader of all technical
                aspects of the business including device schematics, PCB production,
                firmware development, and API definition.
            \item Worked with potential customers to identify bugs and wanted features,
                translating into actionable items to improve product.
            \item Provided support and guidance to Marketing team to track and derive
                various metrics.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{JungleDisk}
            {2016 -- 2018} % chktex 8
            {San Antonio, TX}
            \begin{rSubsubsection}{Senior Developer / Architect}
                {2016 -- 2018} % chktex 8
            \item Spearheaded the efforts to modernize the desktop client build system
                from separate platform specific systems to shared CMake based system.
            \item Provide Architecture and Deployment assistance transitioning services
                off dedicated bare metal into containers.
            \item Lead migration of client data from Rackspace Cloud Files to Google
                Storage.
            \end{rSubsubsection}
        \end{rSubsection}

        \begin{rSubsection}{Rackspace Hosting}
            {2007 -- 2016} % chktex 8
            {San Antonio, TX}
            \begin{rSubsubsection}{Senior SDN Developer}
                {2013 -- 2016} % chktex 8
            \item Lead a team of five in the design and deployment of software defined
                networking products for the leading managed hosting company’s Public
                Cloud, with responsibility for providing secure bridged publicnet and
                servicenet connectivity, and serving as development lead in the effort
                to decouple from vendor-controlled connectivity
            \item Research and implement OpenFlow controllers to provide floating IP
                connectivity from public internet IP space onto isolated private networks
            \item Implement VIF-to-VIF L2 connectivity via STT and VxLAN encapsulation
                coordinated through BGP and EVPN
            \end{rSubsubsection}

            \begin{rSubsubsection}{Ozone Openstack Developer}
                {2011 -- 2013} % chktex 8
            \item Worked on a wide range of projects for the Rackspace Openstack platform,
                including Nova, Quantam, Melange (core-dev), and Openstack-Common
            \item Re-wrote most of the Nova networking code to allow for external services
                (Quantum/Neutron) to control network allocation and management
            \item Bootstrapped the Openstack-Common project to centralize code common to
                multiple Openstack projects, reducing copy-and-paste bit-rot
            \item Created the Openstack-Nose project to provide common test output across
                Openstack projects as a nose plugin, enabling test failures to be masked
                when previously each project was subclassing TestRunner directly
            \item Provide technical leadership to the product management team and junior
                developers for the Cloud Networks initiative following Agile and iterative
                development methods
            \end{rSubsubsection}

            \begin{rSubsubsection}{Backup Automation Developer}
                {2007 -- 2011} % chktex 8
            \item Developed applications and tools to administer and troubleshoot backup
                and storage offerings, including backup failure notification, backup
                set management, tape tracking, storage reporting, and storage provisioning
            \item Grew position from a sole-contributor role to a team of four developers
                during four years in role
            \item Re-designed and implemented a backup reporting database, including
                consolidation of data from more than 50 MSSQL servers into a single
                reporting database, allowing for arbitrary queries to be run against the
                set of MSSQL servers and aggregating/normalizing into consistent formats
            \item Initiated, architected, and assisted in the development of the “Holland
                Backup System” to replace legacy MySQL backup solution, including creation
                of a council of developers and advocates to lead the project, coordination
                and hosting of Code-Jams to bootstrap the project, and championing open
                sourcing efforts
            \item Led the backup platform migration from Legato to Commvault for more than
                10,000 servers, developed application and tooling scripts to automate
                90\% of the migration, and created guidelines for QC/QA efforts
            \end{rSubsubsection}
        \end{rSubsection}
    \end{rSection}

    \begin{rSection}{Patents}
        {\small
        \bigskip
        \mdfdefinestyle{techskills}{innerleftmargin=0.5em,innerrightmargin=0.5em}
        \begin{tabular}{l l}
            {\bf US 9141410} & Pluggable allocation in a cloud computing system \\
            {\bf US 9628328} & Network controller with integrated resource management
            capability \\
            {\bf US 9967111} & Software-defined multinetwork bridge \\
        \end{tabular}
        }
    \end{rSection}
\end{document}
